Reproducible, flexible and high throughput data extraction from primary literature: The \pkg{metaDigitise} \proglang{R} package \vskip15pt Supplementary Materials

### 2018-10-02 docs/MEE_submission/manuscript_MEE.tex
MS tweaks
another MS tweak

\section{Software Validation}
In order to evaluate the consistency of digitisation with \pkg{metaDigitise} between users, fourteen people digitized sets of 14 identical images created from a simulated dataset (see supplements). We found no evidence for any inter-observer variability in digitisations for the mean (ICC = 0, 95\% CI = 0 to 0.029, \textit{p} $>$ 0.999), SD (ICC = 0, 95\% CI = 0 to 0.033, \textit{p} $>$ 0.999) or correlation coefficient (ICC = 0.053, 95\% CI = 0 to 0.296, \textit{p} = 0.377). There was little bias between digitised and true values, on average 1.63\% (mean = 0.02\%, SD = 4.9\%, \textit{r} = -0.03\%) and there were small absolute differences between digitised and true values, on average 2.18\% (mean = 0.40\%, SD = 5.81\%, \textit{r} = 0.33\%) across all three descriptive statistics. SD estimates from digitisations are clearly most error prone. The mean absolute differences for each plot type clearly show that this effect is driven by extraction from box plots and histograms (\% difference; box plot: 15.81, histogram: 5.21, mean/error: 1.50, scatter plot: 0.43). SD estimation from box plot descriptive statistics is known to be more error prone, especially at small sample sizes \citep{Wan2014}.

@@

Although \pkg{metaDigitise} is very flexible and provides functionality not seen in any other package, there are some functions that it does not perform (see Table \ref{tab:comparison}). Notably \pkg{metaDigitise} lacks automated point detection. However, from our experience, manual digitising is more reliable and often equally as fast. Given the variation in image quality, calibration for automatic point detection needs to be done for each figure individually. Additionally, auto-detection often misses points which then need to be manually added. Based on tests of \pkg{metaDigitise} (see above), figures can be extracted in around 1-2 minutes, including the entry of metadata. As a result, we do not believe that current automated point detection techniques provide substantial benefits in terms of time or accuracy.

>>>>

\section{Software Validation}
To evaluate the consistency of digitisation with \pkg{metaDigitise} between users, fourteen people digitized sets of 14 identical images created from a simulated dataset (see supplements). We found no evidence for any inter-observer variability in digitisations for the mean (ICC = 0, 95\% CI = 0 to 0.029, \textit{p} $>$ 0.999), SD (ICC = 0, 95\% CI = 0 to 0.033, \textit{p} $>$ 0.999) or correlation coefficient (ICC = 0.053, 95\% CI = 0 to 0.296, \textit{p} = 0.377). There was little bias between digitised and true values, on average 1.63\% (mean = 0.02\%, SD = 4.9\%, \textit{r} = -0.03\%) and there were small absolute differences between digitised and true values, on average 2.18\% (mean = 0.40\%, SD = 5.81\%, \textit{r} = 0.33\%) across all three descriptive statistics. SD estimates from digitisations are clearly most error prone. The mean absolute differences for each plot type clearly show that this effect is driven by extraction from box plots and histograms (\% difference; box plot: 15.81, histogram: 5.21, mean/error: 1.50, scatter plot: 0.43). SD estimation from box plot descriptive statistics is known to be more error prone, especially at small sample sizes \citep{Wan2014}.

@@

Although \pkg{metaDigitise} is very flexible and provides functionality not seen in any other package, there are some functions that it does not perform (see Table \ref{tab:comparison}). Notably \pkg{metaDigitise} lacks automated point detection. However, from our experience, manual digitising is more reliable and often equally as fast. Given the variation in image quality, calibration for automatic point detection needs to be done for each figure individually. Additionally, auto-detection often misses points which then need to be manually added. Based on tests of \pkg{metaDigitise} (see above), figures can be extracted in around 1-2 minutes, including the entry of metadata. As a result, we do not believe that current automated point detection techniques provide substantial benefits in terms of time or accuracy. 
Indeed, in a recent project developing automated point extraction techniques, only 15/136 (11\%) of studies screened contained figures suitable for the presented method, and in only 12/27 (44\%) of the resulting figures was the data correctly extracted \citep{Hartgerink2017}.
